Manuscript

### 2017-06-16 manuscript.Rmd
Converted and loaded in the five remaining geojson files

```{r load_data}
denver_tracts <- geojson_read("data/denver_tracts.geojson", what = "sp")

```

>>>>

```{r load_data}
denver_tracts <- geojson_read("data/denver_tracts.geojson", what = "sp")
denver_parks <- geojson_read ("data/denver_parks.geojson", what = "sp")

boston_tracts <- geojson_read("data/boston_tracts.geojson", what = "sp")
boston_parks <- geojson_read("data/boston_parks.geojson", what = "sp")

nyc_tracts <- geojson_read("data/nyc_tracts.geojson", what = "sp")
nyc_parks <- geojson_read("data/nyc_parks.geojson", what = "sp")
```
